Modelling the emergence of whisker barrels

### 2020-06-19 paper/briefpaper/brief.tex
sw edits

% Some document-defined commands
\newcommand*\dif{\mathop{}\!\mathrm{d}}
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
\newcommand{\stu}[1]{\textcolor{red}{#1}}
\newcommand{\dvrg}{\nabla\vcdot\nabla}
\newcommand{\e}{\emph}
\newcommand{\bol}{\textbf}
\newcommand{\mb}[1]{\mathbf{#1}}
\makeatletter
\newcommand*\vcdot{\mathpalette\vcdot@{.35}}
\newcommand*\vcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\newcommand{\code}[1]{\textsf{#1}}
% Nice norms:
\usepackage{mathtools}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
% Degrees symbol:
\usepackage{textcomp}

@@

\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig1.png}
    \caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1
      by \cite{zheng_signal_2001}, with black lines to delineate barrels and to
      measure departure (Honda-$\delta$; see \citealp{senft_mouse_1991}) from a
      perfect Voronoi tesselation. Right shows the initial distribution of axon
      branching density ($a$) for one thalamocortical projection, and two
      molecular guidance fields ($\rho$), \cmnt{where the domain $S$ has been
        traced from \textbf{A}}. \textbf{B} The strengths of interaction
      $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41
      projections by the lengths of green and blue arrows respectively, assuming
      that similar fields aligned to the posterior-anterior and medial-lateral
      axes in the ventroposterior medial nucleus of the thalamus are sampled at
      the locations of putative barreloid centers (reconstructed from
      \citealp{haidarliu_size_2001}, \cmnt{Fig.\,5b}). \textbf{C} Simulation results for parameters
      \cmnt{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
      $\epsilon=1.2$} and $\delta{t}=0.0001$. Colours indicate the thalamic
      projection for which the connection density is maximal and black lines
      delineate boundaries (see Movie
      S1). \textbf{D} Red dots show the Honda metric, \cmnt{$\delta(t)$}, obtained from \stu{the}
      simulation approaching that obtained from \cmnt{real} barrels in \textbf{A} (dotted
      line); black squares \cmnt{provide a} measure \cmnt{of} the correspondence
      between the real and
      simulated barrel shapes, $\eta(t)$ (the \cmnt{pattern quality metric---see
        Materials \& Methods; units mm$^3$});
      \cmnt{grey hexagons \stu{provide a measure of how selectively each
          cortical site is innervated};
        $\omega(t) = \oiint_{S} \mu(\mb{x},t) \mathrm{d}S$, where
        $\mu(\mb{x}) \equiv \mathrm{max}_i\big(c_i(\mb{x},t)\big)\big/\sum_{j=1}^{N} c_j(\mb{x},t)$.}
      \textbf{E} \stu{Plotted across the cortical sheet, the selectivity
        develops to reveal an alignment with the emergent barrel boundary
        shapes}. \cmnt{The colour map
        indicates the values of $\mu(\mb{x})$. Overlaid
        contours show $c_i > 0.95 \mathrm{max}_i\big(c_i(\mb{x})\big)$.} All scale bars 1\,mm.}
    \label{fig:main}
  \end{fullwidth}
\end{figure}

@@

The only differences between thalamic projections are their strengths of
interaction with the guidance fields, $\gamma$, hence any reliable differences
between emergent cortical fields must be due to differences in these values
only. We speculate that the contribution of a given ephrin field, to the
velocity at which a projection migrates across the cortical subplate, is
determined by the concentration of a similar molecule at its thalamic origin,
i.e., the putative barreloid center. \stu{As such, we consider linear gradients aligned to anterior-posterior and medial-lateral axes through the VPM, and as $\gamma$-values use the coordinates of the barreloid centers in these axes as they appear in \citep{haidarliu_size_2001} (Fig.\,\ref{fig:main}B).} \stu{Complementary thalamic and cortical molecular guidance gradients of this form have been well established experimentally} \citep{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}, \stu{e.g., cells originating in the medial part of ventrobasal thalamus (comprising VPM and VPL) express high levels of EphA receptors and project to the lateral part of S1, which expresses low levels of ephrin-A5, and cells originating in the lateral part of ventrobasal thalamus express low levels of EphA receptors and project to the medial part of S1, which expresses high levels of ephrin-A5 (see} \citealp{gao_regulation_1998,dufour_area_2003,vanderhaeghen_developmental_2004,speer_grading_2005}).

A cortical boundary enclosing 41 \cmnt{macrovibrissae} barrels was traced from
a cytochrome oxidase stain from \cite{zheng_signal_2001} \cmnt{(using the
  authors' original data)}, and Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved
for $N=41$ projections on the resulting domain, using $M=2$ linear signalling
gradients aligned with the anterior-posterior and medial-lateral axes. From
random initial conditions for $a(\mb{x},0)$, \cmnt{with each hexagonal element
  of $a_i$ set from a uniform distribution according to $0.2+{U}(0,0.2)$, and
  $c(\mb{x},0)=0$}, a clear Voronoi-like tesselation
emerged (Fig.\,\ref{fig:main}C; see Movie S1). A reduction in the Honda delta
metric (see \citealp{senft_mouse_1991}) confirmed that a `good' Voronoi
pattern emerged within \cmnt{$\approx$~20000} iterations
(Fig.\,\ref{fig:main}D).  A measure of the difference in \cmnt{barrel area}
between real and simulated barrels revealed a strong correspondence (see
Fig.\,\ref{fig:main}D, squares). \cmnt{In a chosen region, the ratio of
  \emph{the connection density of the TC type $i$ which makes the densest
    connections} to \emph{the sum of all connection densities} gives a measure
  of the selectivity of the connection density, $\mu(\mb{x},t)$. We summed this measure
  across the entire barrel domain and named it $\omega(t)$ (see
  Fig.\,\ref{fig:main}D, grey hexagons). $\omega$ increases during the first
  20000 simulation steps and converges on a stable
  value. Fig.\,\ref{fig:main}E shows the selectivity measure plotted as a
  luminance map, giving a more graded impression of the structure which
  develops in the system.}

% Full page width
\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig2.png}
    \caption{\cmnt{\textbf{A} Exploring the parameter space of the model given
        in Eqs.\,1--3. Graphs show the three pattern metrics for $t=30000$
        steps as colourmaps: Honda $\delta$ (top row) shows conformance to a
        Voronoi pattern; $\eta$ (middle row) gives the simulated/experimental
        barrel area difference and $\omega$ (bottom row) is a measure of
        selectivity of the connection densities for the 41
        thalamocortical axon types. For each row, lighter (orange/yellow)
        colours imply a better model. The parameter space explored is three
        dimensional with the parameter ratio $\alpha/\beta$ varied along the
        columns of graphs, the competition parameter $\epsilon$ varied on the
        $y$-axes and the diffusion constant, $D$ varied along the $x$-axes. An
        asterisk (*) marks the parameter set displayed in
        Fig.\,\ref{fig:main}. Boxes i), ii)~and iii)~mark parameter sets for which
        corresponding patterns are shown in \textbf{B} (for $t=30000$ steps).}}
    \label{fig:paramsweep}
  \end{fullwidth}
\end{figure}

\cmnt{To determine the robustness of the model to its parameters, we
  investigated its behaviour with respect to changes in the parameters $D$,
  $\epsilon$ and the ratio of $\alpha$ to $\beta$. Fig.\,\ref{fig:paramsweep}A
  shows the value of the metrics $\delta$, $\eta$ and $\omega$ after $30000$
  iterations plotted as colour maps for $216$ parameter sets. Each row of maps
  shows the results for a separate metric. Each column of maps shows
  results for a different value of the ratio $\alpha / \beta$. The diffusion
  parameter, $D$ varies with the $x$ axes and the strength of competition,
  $\epsilon$ varies with the $y$ axes. The colour maps are arranged so that
  `yellow is good'. Lower values of $\delta$ indicate good Voroni patterns and
  are yellow. Lower values of the difference between real and simulated barrel
  area indicates good pattern matching. Higher values of $\omega$ indicate
  greater selectivity and are coloured yellow. White squares indicate that the
  simulation was not stable for that parameter set.}

\cmnt{The maps indicate that the pattern is not strongly influenced by the
  choice of $\alpha/\beta$, which was varied by 5 orders of magnitude. The
  most Voronoi-like patterns were achieved for parameter sets for which $D$
  and $\epsilon$ were high. The barrel area metric, $\eta$ indicates a strong
  preference for $D\approx0.5$, although this does not give the
  solution of maximum selectivity, which for $D$ should be small. Thus, there is a
  trade-off between good selection and good Voroni pattern
  conformation. The
  parameter set indicated by the asterisk in
  Fig.\,\ref{fig:paramsweep}A is presented in Fig.\,\ref{fig:main} because it
  provides the best barrel area correspondence and produces a good Voronoi
  pattern. In Fig.\,\ref{fig:paramsweep}B, we present some patterns
  representing alternative parameter choices. Fig.\,\ref{fig:paramsweep}B i)
  shows the simulation result with low diffusion constant, $D$. Reducing the
  diffusion constant is equivalent to increasing the size of the domain $S$
  and so this simulation can be thought to represent an animal with a large
  cortical area but with unchanged cortical complexity. In this simulation, a
  large proportion of the domain is occupied by the projections with
  intermediate interaction parameters; those with strong interaction
  parameters are bunched up towards the edge of the domain. A barrel pattern
  fails to form. Fig.\,\ref{fig:paramsweep}B ii)~and iii)~indicate the effect
  of varying $D$ in either direction from its optimum. ii)~is a less
  exaggerated version of the pattern in i), whereas iii)~shows an expansion of
  the outer barrels and a corresponding compression of the barrels within.}

% Full page width
\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig3.png}
    \caption{
      \cmnt{\textbf{A} Sensitivity of the system pattern
        metrics $\delta(t)$ (top row), $\omega(t)$ (middle row) and $\eta(t)$
        (bottom row), evaluated at $t=30000$ steps,
        to three classes of perturbation. $y$-axes and colour scales have identical ranges
        to the colour scales in Fig.\,\ref{fig:paramsweep}, to ease comparison
        with the parameter exploration.
        %
        \emph{Column 1:} Random noise drawn from a uniform distribution,
        $(\gamma_{max}-\gamma_{min})\,U(0,\nu_\gamma)$, added
        to the values for the interaction parameters, $\gamma_{i,j}$ used in
        Fig.\,\ref{fig:main}.
        %
        \emph{Column 2:} Random noise $(\rho_{max} - \rho_{min})\,U(0, \nu_{\rho})$
        was added to each hex element of $\rho_1(\mb{x})$ and $\rho_2(\mb{x})$ and the result
        was smoothed by convolution with a symmetric 2D
        Gaussian kernel of width $\sigma_\rho$. Colour maps in this column
        thus show the effect of changing the magnitude and the length scale of
        noise in the guidance fields.
        %
        \emph{Column 3:} Colour maps show the result of setting the rotational angle
        of the linearly varying guidance field, $\rho_1(\mb{x})$, to $\phi_{\rho_1}$,
        and modifying its overall gain to $G_{\rho_1}$, whilst keeping the
        parameters of $\rho_2(\mb{x})$
        unchanged from those used in the simulation in
        Fig.\,\ref{fig:main}, for which $\phi_{\rho_1}=6$\textdegree~and
        $\phi_{\rho_2}=84$\textdegree.
        %
        \textbf{B} Four ways in which the perturbations in \textbf{A} affect
        the patterns. i) The effect of significant interaction parameter noise
        causes barrels to become swapped from the positions they would
        otherwise take. ii) High magnitude, short lengthscale noise in
        $\rho(\mb{x})$ leads to `wiggly' boundaries between barrels. iii)
        Shows the effect of reducing the slope of $\rho_1$ (by a factor of 10)
        which reduces the strength of the axons' interaction with the guidance
        field in the left-right sense. Barrel rows B, C and D become `crushed'
        down the center line, and edge barrels dominate. iv) The effect of
        rotating $\rho_1$ by 20\textdegree~is a relatively mild distortion of
        the pattern in the anticlockwise sense.
      }
    }
    \label{fig:sens}
  \end{fullwidth}
\end{figure}

\cmnt{We performed a sensitivity analysis to determine if the quality of the
  pattern was affected by perturbations to any of the following inputs:
%
  i)~the magnitude and offset of the noise applied to $a_i$ at $t=0$;
%
  ii)~random noise applied to the interaction parameters, $\gamma_{i,j}$;
%
  iii)~random noise (at various length scales) applied to the guidance fields;
%
  and
%
  iv)~The angle and magnitude of one of the guidance fields, ($\rho_1$;
  Fig.\,\ref{fig:main}A).
%
  In the following analysis, we always evaluated the three pattern metrics,
  $\delta$ (the Honda Voronoi metric), $\eta$ (the pattern-match metric) and
  $\omega$ (which measures selectivity of connections, $c_i$) after running
  the model for 30000 simulation steps.}

\cmnt{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  three metrics in the default model. The
  results (where deviations occur as a result of the different random initial
  conditions for $a_i$) were $\delta=0.089\,(0.004)$, $\eta=0.2108\,(0.002)$ and
  $\omega=0.2165\,(0.0001)$. None of the three metrics were strongly affected
  by the random changes to $a_i$ on each run. The results give a baseline from
  which to evaluate whether changes in the other inputs have a statistically
  significant effect.}

\cmnt{Next, we modified the parameters of the generating uniform distribution
  to initialize $a_i$ for each hex to $0.1+{U}(0,0.4)$ (increasing the variability of
  $a_i(\mb{x},t=0)$ without changing the mean initial activation). We ran this
  system 10 times and obtained the results $\delta=0.090\,(0.005)$,
  $\eta=0.2136\,(0.004)$ and $\omega=0.2166\,(0.0003)$. Paired two-sample t-tests
  demonstrated that the increase in noise amplitude made no significant
  difference to the metric results ($\delta:
  \mathrm{t}=-0.69,\mathrm{p}=0.49$,
  $\eta: \mathrm{t}=-2.0,\mathrm{p}=0.06$,
  $\omega: \mathrm{t}=-1.7,\mathrm{p}=0.11$). 10 runs of a
  noise-free initial condition with $a_i=0.3$ for every hex showed that
  the model is deterministic (all runs produced the results $\delta=0.0928$,
  $\eta=0.21236$ and $\omega=0.21649$) and that stochasticity in
  $a_i(\mb{x},t=0)$ is not required by this model, as all three results lay within
  one standard deviation of those for the runs in which $a_i$ was initialized stochastically.}

% Quick check that noise free result is within 1 SD for the noisier initial conditions
%         Noisefree    Normal noise    NF SD from Normal?   Noisy            NF SD from Noisy?
% delta   0.0928       0.089(0.004)    <1                   0.090 (0.005)    <1
% eta     0.2124       0.2108(0.002)   <1                   0.2136 (0.004)   <1
% omega   0.21649      0.2165(0.0001)  <1                   0.2166 (0.0003)  <1

\cmnt{Fig\,\ref{fig:sens}A shows the results for perturbations ii) to iv). The
  first column shows the results for the three metrics where the interaction
  parameters $\gamma_{i,j}$ are replaced by $\gamma_{i,j}'$ according to
  $\gamma_{i,j}' = \gamma_{i,j} + U(0,4\nu_\gamma)$, where $\nu_\gamma$ is the
  chosen magnitude of the noise (the proportion of the full range of
  $\gamma_{i,j}$, which is 4). The Voronoi nature of the pattern ($\delta$)
  and the selectivity of the fields are not strongly affected by interaction
  parameter noise, but the pattern metric, $\eta$ shows a... ADD SUB GRAPH.}

@@

@@

>>>>

% Some document-defined commands
\newcommand*\dif{\mathop{}\!\mathrm{d}}
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
\newcommand{\stu}[1]{\textcolor{red}{#1}}
\newcommand{\dvrg}{\nabla\vcdot\nabla}
\newcommand{\e}{\emph}
\newcommand{\bol}{\textbf}
\newcommand{\mb}[1]{\mathbf{#1}}
\makeatletter
\newcommand*\vcdot{\mathpalette\vcdot@{.35}}
\newcommand*\vcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\newcommand{\code}[1]{\textsf{#1}}
% Nice norms:
\usepackage{mathtools}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}

@@

\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig1.png}
    \caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1
      by \cite{zheng_signal_2001}, with black lines to delineate barrels and to
      measure departure (Honda-$\delta$; see \citealp{senft_mouse_1991}) from a
      perfect Voronoi tesselation. Right shows the initial distribution of axon
      branching density ($a$) for one thalamocortical projection, and two
      molecular guidance fields ($\rho$), \cmnt{where the domain $S$ has been
        traced from \textbf{A}}. \textbf{B} The strengths of interaction
      $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41
      projections by the lengths of green and blue arrows respectively, assuming
      that similar fields aligned to the posterior-anterior and medial-lateral
      axes in the ventroposterior medial nucleus of the thalamus are sampled at
      the locations of putative barreloid centers (reconstructed from
      \citealp{haidarliu_size_2001}, \cmnt{Fig.\,5b}). \textbf{C} Simulation results for parameters
      \cmnt{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
      $\epsilon=1.2$} and $\delta{t}=0.0001$. Colours indicate the thalamic
      projection for which the connection density is maximal and black lines
      delineate boundaries (see Movie
      S1). \textbf{D} Red dots show the Honda-$\delta$ metric obtained from \stu{the}
      simulation approaching that obtained from \cmnt{real} barrels in \textbf{A} (dotted
      line); black squares \cmnt{give a} measure \cmnt{of} the correspondence
      between the real and
      simulated barrel shapes, $\eta$ (the \cmnt{pattern quality metric---see
        Materials \& Methods; units mm$^3$});
      \cmnt{grey hexagons \stu{provide a measure of how selectively each
          cortical site is innervated} OR: show the measure of localization, $\omega =
        \oiint_{S} \left( \mathrm{max}_i(c_i)/\sum_{i=1}^{N} c_i\right) \mathrm{d}S$. }
      \textbf{E} \stu{Plotted across the cortical sheet, the selectivity
        develops to reveal an alignment with the emergent barrel boundary
        shapes} OR: \cmnt{The localization measure plotted across the domain
        shows that the structure in the connection density which has developed
        by $t=30000$ is largely absent at $t=1000$. The
        colour map
        indicates the values of  $\mathrm{max}_i(c_i)/\sum_{i=1}^{N} c_i$. Overlaid
        contours show $c_i > 0.95 \mathrm{max}_i(c_i)$.} All scale bars 1\,mm.}
    \label{fig:main}
  \end{fullwidth}
\end{figure}

@@

The only differences between thalamic projections are their strengths of
interaction with the guidance fields, $\gamma$, hence any reliable differences
between emergent cortical fields must be due to differences in these values
only. We speculate that the contribution of a given ephrin field, to the
velocity at which a projection migrates across the cortical subplate, is
determined by the concentration of a similar molecule at its thalamic origin,
i.e., the putative barreloid center. \stu{As such, we consider linear gradients aligned to anterior-posterior and medial-lateral axes through the VPM, and as $\gamma$-values use the coordinates of the barreloid centers in these axes as they appear in \citep{haidarliu_size_2001} (Fig.\,\ref{fig:main}B).} \stu{Complementary thalamic and cortical molecular guidance gradients of this form have been well established experimentally \citep{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}, e.g., cells originating in the medial part of ventrobasal thalamus (comprising VPM and VPL) express high levels of EphA receptors and project to the lateral part of S1, which expresses low levels of ephrin-A5, and cells originating in the lateral part of ventrobasal thalamus express low levels of EphA receptors and project to the medial part of S1, which expresses high levels of ephrin-A5 (see Gao, 1998; Dufour et al., 2003; Vanderhaegen \& Polleux, 2004; Speer \& Chapman, 2005).} \stu{We concentrate on the representation of the 41 macrovibrissae because their thalamic and cortical correlates are easily identifiable and consistently positioned, we exclude the microvibrissae to limit the complexity of the simulations, and we exclude the five rhinal whiskers as their representation in S1 is isolated from the main barrel field.} A cortical boundary enclosing \stu{the} 41 \cmnt{macrovibrissae} barrels was traced from
a cytochrome oxidase stain from \cite{zheng_signal_2001} \cmnt{(using the
  authors' original data)}, and Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved
for $N=41$ projections on the resulting domain, using $M=2$ linear signalling
gradients aligned with the anterior-posterior and medial-lateral axes.

\stu{From}
random initial conditions for $a(\mb{x},0)$, \cmnt{with each hexagonal element
  of $a_i$ set from a uniform distribution according to $0.2+{U}(0,0.2)$, and
  $c(\mb{x},0)=0$}, a clear Voronoi-like tesselation
emerged (Fig.\,\ref{fig:main}C; see Movie S1). A reduction in the Honda delta
metric (see \citealp{senft_mouse_1991}) confirmed that a `good' Voronoi
pattern emerged within \cmnt{$\approx$~20000} iterations
(Fig.\,\ref{fig:main}D).  A measure of the difference in \cmnt{barrel area}
between real and simulated barrels revealed a strong correspondence (see
Fig.\,\ref{fig:main}D, squares). \cmnt{In a chosen region, the ratio of
  \emph{the connection density of the TC type $i$ which makes the densest
    connections} to \emph{the sum of all connection densities} gives a measure
  of the localization of the connection density. We computed this measure
  across the entire barrel domain and named it $\omega$ (see
  Fig.\,\ref{fig:main}D, grey hexagons). $\omega$ increases during the first
  20000 simulation steps and converges on a stable
  value. Fig.\,\ref{fig:main}E shows the localization measure plotted as a
  luminance map, giving a more graded impression of the structure which
  develops in the system.}

% Full page width
\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig2.png}
    \caption{\cmnt{\textbf{A} Exploring the parameter space of the model given
        in Eqs.\,1--3. Graphs show the three pattern metrics for $t=30000$
        steps as colourmaps: Honda $\delta$ (top row) shows conformance to a
        Voronoi pattern; $\eta$ (middle row) gives the simulated/experimental
        barrel area difference and $\omega$ (bottom row) is a measure of
        localization (separation) of the connection densities for the 41
        thalamocortical axon types. For each row, lighter (orange/yellow)
        colours imply a better model. The parameter space explored is three
        dimensional with the parameter ratio $\alpha/\beta$ varied along the
        columns of graphs, the competition parameter $\epsilon$ varied on the
        $y$-axes and the diffusion constant, $D$ varied along the $x$-axes. An
        asterisk (*) marks the parameter set displayed in
        Fig.\,\ref{fig:main}. Boxes i), ii)~and iii)~mark parameter sets for which
        corresponding patterns are shown in \textbf{B} (for $t=30000$ steps).}}
    \label{fig:paramsweep}
  \end{fullwidth}
\end{figure}

\cmnt{To determine the robustness of the model to its parameters, we
  investigated its behaviour with respect to changes in the parameters $D$,
  $\epsilon$ and the ratio of $\alpha$ to $\beta$. Fig.\,\ref{fig:paramsweep}A
  shows the value of the metrics $\delta$, $\eta$ and $\omega$ after $30000$
  iterations plotted as colour maps for $216$ parameter sets. Each row of maps
  shows the results for a separate metric. Each column of maps shows
  results for a different value of the ratio $\alpha / \beta$. The diffusion
  parameter, $D$ varies with the $x$ axes and the strength of competition,
  $\epsilon$ varies with the $y$ axes. The colour maps are arranged so that
  `yellow is good'. Lower values of $\delta$ indicate good Voroni patterns and
  are yellow. Lower values of the difference between real and simulated barrel
  area indicates good pattern matching. Higher values of $\omega$ indicate
  better localization and are coloured yellow. White squares indicate that the
  simulation was not stable for that parameter set.}

\cmnt{The maps indicate that the pattern is not strongly influenced by the
  choice of $\alpha/\beta$, which was varied by 5 orders of magnitude. The
  most Voronoi-like patterns were achieved for parameter sets for which $D$
  and $\epsilon$ were high. The barrel area metric, $\eta$ indicates a strong
  preference for $D\approx0.5$, although this does not give the maximally
  localized solution, which for $D$ should be small. Thus, there is a
  trade-off between good localization and good Voroni pattern
  conformation. The
  parameter set indicated by the asterisk in
  Fig.\,\ref{fig:paramsweep}A is presented in Fig.\,\ref{fig:main} because it
  provides the best barrel area correspondence and produces a good Voronoi
  pattern. In Fig.\,\ref{fig:paramsweep}B, we present some patterns
  representing alternative parameter choices. Fig.\,\ref{fig:paramsweep}B i)
  shows the simulation result with low diffusion constant, $D$. Reducing the
  diffusion constant is equivalent to increasing the size of the domain $S$
  and so this simulation can be thought to represent an animal with a large
  cortical area but with unchanged cortical complexity. In this simulation, a
  large proportion of the domain is occupied by the projections with
  intermediate interaction parameters; those with strong interaction
  parameters are bunched up towards the edge of the domain. A barrel pattern
  fails to form. Fig.\,\ref{fig:paramsweep}B ii)~and iii)~indicate the effect
  of varying $D$ in either direction from its optimum. ii)~is a less
  exaggerated version of the pattern in i), whereas iii)~shows an expansion of
  the outer barrels and a corresponding compression of the barrels within.}

% Full page width
\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig3.png}
    \caption{\cmnt{Sensitivity analysis. Column \textbf{A} shows...}}
    \label{fig:sens}
  \end{fullwidth}
\end{figure}

\cmnt{We performed a sensitivity analysis to determine if the quality of the
  pattern was affected by perturbations to any of the following inputs:
%
  i)~the magnitude and offset of the noise applied to $a_i$ at $t=0$;
%
  ii)~random noise applied to the interaction parameters, $\gamma_{i,j}$;
%
  iii)~random noise (at various length scales) applied to the guidance fields;
%
  and
%
  iv)~The angle and magnitude of one of the guidance fields, ($\rho_1$;
  Fig.\,\ref{fig:main}A).
%
  In the following analysis, we always evaluated the three pattern metrics,
  $\delta$ (the Honda Voronoi metric), $\eta$ (the pattern-match metric) and
  $\omega$ (which measures localization of connections, $c_i$) after running
  the model for 30000 simulation steps.}

\cmnt{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  three metrics in the default model. The
  results (where deviations occur as a result of the different random initial
  conditions for $a_i$) were $\delta=0.089\,(0.004)$, $\eta=113.5\textbf{!!}\,(1.2)$ and
  $\omega=0.2165\,(0.0001)$. None of the three metrics were strongly affected
  by the random changes to $a_i$ on each run. The results give a baseline from
  which to evaluate whether changes in the other inputs have a statistically
  significant effect.}

\cmnt{Next, we modified the parameters of the generating uniform distribution
  to initialize $a_i$ for each hex to $0.1+{U}(0,0.4)$ (increasing the variability of
  $a_i(\mb{x},t=0)$ without changing the mean initial activation). We ran this
  system 10 times and obtained the results $\delta=0.090\,(0.005)$,
  $\eta=115\,(1.9)\textbf{!!}$ and $\omega=0.2166\,(0.0003)$. Paired two-sample t-tests
  demonstrated that the increase in noise amplitude made no significant
  difference to the metric results ($\delta:
  \mathrm{t}=-0.69,\mathrm{p}=0.49$,
  $\eta: \mathrm{t}=-2.0,\mathrm{p}=0.06\textbf{!!}$,
  $\omega: \mathrm{t}=-1.7,\mathrm{p}=0.11$). 10 runs of a
  noise-free initial condition with $a_i=0.3$ for every hex showed that
  the model is deterministic (all runs produced the results $\delta=0.0928$,
  $\eta=114.31\textbf{!!}$ and $\omega=0.21649$) and that stochasticity in
  $a_i(\mb{x},t=0)$ is not required by this model, as all three results lay within
  one standard deviation of those for the runs in which $a_i$ was initialized stochastically.}

% Quick check that noise free result is within 1 SD for the noisier initial conditions
%         Noisefree    Normal noise    NF SD from Normal?   Noisy            NF SD from Noisy?
% delta   0.0928       0.089(0.004)    <1                   0.090 (0.005)    <1
% eta     114.31       113.5(1.2)      <1                   115 (1.9)        <1
% omega   0.21649      0.2165(0.0001)  <1                   0.2166 (0.0003)  <1

\cmnt{Fig\,\ref{fig:sens}A shows the results for perturbations ii) to iv). The
  first column shows the results for the three metrics where the interaction
  parameters $\gamma_{i,j}$ are replaced by $\gamma_{i,j}'$ according to
  $\gamma_{i,j}' = \gamma_{i,j} + U(0,4\nu_\gamma)$, where $\nu_\gamma$ is the
  chosen magnitude of the noise (the proportion of the full range of
  $\gamma_{i,j}$, which is 4). The Voronoi nature of the pattern ($\delta$)
  and the localization of the fields are not strongly affected by interaction
  parameter noise, but the pattern metric, $\eta$ shows a... ADD SUB GRAPH.}

@@

\stu{In reality, scores of smaller Dirichletform barrels representing the microvibrissae form to the right of where the E-row barrels emerge in our simulations, presumably via the same competitive processes. Enforcing here the same boundary condition as used to represent the true edges of the barrel field is necessary to ensure the stability of the simulation, though we acknowledge that this region of the boundary is enforced primarily to keep the number of simulated projections, and hence the overall computational complexity of the simulation, manageable (simulating each additional projection introduces an extra \textbf{YYY} new dynamical variables).}

@@

% NOTES
